Online {\IterComp}

### 2017-09-16 related.tex
minor

\subsection{{\IterComp}}
Multiple different adaptive compilation techniques have been proposed for finding a near optimal combination of optimization
settings~\cite{agakov06,hoste2008cole,kulkarni04,stephenson03} by probabilistically searching the space of possible combinations. But with
all of them there is uncertainty about whether the quality of their results depends on the data set used. Chen~\etal~\cite{chen10,chen12a}
examined this issue and showed that indeed the best optimization options differ across inputs. Still, in most cases it is possible to find
a combination of optimizations that produces good results across all inputs, by using a few tens of inputs to evaluate our optimizations
on. While a positive result, this is still impractical. Producing tens of realistic input sets might be difficult. Even if not, each
combination of optimization options has to be evaluated on every input set, increasing the time \itercomp takes by at least an order of
magnitude.

>>>>

\subsection{{\IterComp}}
Various adaptive compilation techniques have been proposed for finding near optimal compilation
settings~\cite{agakov06,kulkarni04,stephenson03}. These approaches evaluate the performance of candidate compiler options through repeated
executions using the same input. All these approaches implicitly assume the found compiler settings work for other unseen datasets.
Chen~\etal~\cite{chen10,chen12a} show that this assumption is not true, and the best optimization options can differ across inputs. Still,
in most cases it is possible to find a combination of optimizations that produces good results across all inputs, by using a few tens of
inputs to evaluate our optimizations on. While a positive result, this is still impractical. Producing tens of realistic input sets might
be difficult. Even if not, each combination of optimization options has to be evaluated on every input set, increasing the time \itercomp
takes by at least an order of magnitude.
